Topic modeling on EU and the USA research projects

### 2017-06-21 thesis_report/draft_thesis.tex
Appendix wordclouds (10/10)

\begin{center}
\begin{figure}
\begin{tabular}{rcl}
\subfloat[Topic 0]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic0_8000.png}} &
\subfloat[Topic 1]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic1_8000.png}}&
\subfloat[Topic 2]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic2_8000.png}}\\
\subfloat[Topic 3]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic3_8000.png}}&
\subfloat[Topic 4]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic4_8000.png}} &
\subfloat[Topic 5]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic5_8000.png}}\\
\subfloat[Topic 6]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic6_8000.png}} &
\subfloat[Topic 7]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic7_8000.png}}&
\subfloat[Topic 8]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic8_8000.png}}\\
\subfloat[Topic 9]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic9_8000.png}}&
\end{tabular}
\caption{Wordclouds of topics of the USA (1994-1997)}
\end{figure}
\end{center}

\begin{center}
\begin{figure}
\begin{tabular}{rcl}
\subfloat[Topic 0]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic0_8000.png}} &
\subfloat[Topic 1]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic1_8000.png}}&
\subfloat[Topic 2]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic2_8000.png}}\\
\subfloat[Topic 3]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic3_8000.png}}&
\subfloat[Topic 4]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic4_8000.png}} &
\subfloat[Topic 5]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic5_8000.png}}\\
\subfloat[Topic 6]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic6_8000.png}} &
\subfloat[Topic 7]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic7_8000.png}}&
\subfloat[Topic 8]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic8_8000.png}}\\
\subfloat[Topic 9]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic9_8000.png}}&
\end{tabular}
\caption{Wordclouds of topics of the USA (1998-2001)}
\end{figure}
\end{center}

\begin{center}
\begin{figure}
\begin{tabular}{rcl}
\subfloat[Topic 0]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic0_8000.png}} &
\subfloat[Topic 1]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic1_8000.png}}&
\subfloat[Topic 2]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic2_8000.png}}\\
\subfloat[Topic 3]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic3_8000.png}}&
\subfloat[Topic 4]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic4_8000.png}} &
\subfloat[Topic 5]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic5_8000.png}}\\
\subfloat[Topic 6]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic6_8000.png}} &
\subfloat[Topic 7]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic7_8000.png}}&
\subfloat[Topic 8]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic8_8000.png}}\\
\subfloat[Topic 9]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic9_8000.png}}&
\end{tabular}
\caption{Wordclouds of topics of the USA (2002-2006)}
\end{figure}
\end{center}

\begin{center}
\begin{figure}
\begin{tabular}{rcl}
\subfloat[Topic 0]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic0_9000.png}} &
\subfloat[Topic 1]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic1_9000.png}}&
\subfloat[Topic 2]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic2_9000.png}}\\
\subfloat[Topic 3]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic3_9000.png}}&
\subfloat[Topic 4]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic4_9000.png}} &
\subfloat[Topic 5]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic5_9000.png}}\\
\subfloat[Topic 6]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic6_9000.png}} &
\subfloat[Topic 7]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic7_9000.png}}&
\subfloat[Topic 8]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic8_9000.png}}\\
\subfloat[Topic 9]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic9_9000.png}}&
\end{tabular}
\caption{Wordclouds of topics of the USA (2007-2013)}
\end{figure}
\end{center}

\begin{center}
\begin{figure}
\begin{tabular}{rcl}
\subfloat[Topic 0]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic0_8000.png}} &
\subfloat[Topic 1]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic1_8000.png}}&
\subfloat[Topic 2]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic2_8000.png}}\\
\subfloat[Topic 3]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic3_8000.png}}&
\subfloat[Topic 4]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic4_8000.png}} &
\subfloat[Topic 5]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic5_8000.png}}\\
\subfloat[Topic 6]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic6_8000.png}} &
\subfloat[Topic 7]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic7_8000.png}}&
\subfloat[Topic 8]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic8_8000.png}}\\
\subfloat[Topic 9]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic9_8000.png}}&
\end{tabular}
\caption{Wordclouds of topics of the USA (2014-2017)}
\end{figure}
\end{center}

>>>>

\begin{center}
\begin{figure}
\begin{tabular}{rcl}
\subfloat[Software engineering]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic0_8000.png}} &
\subfloat[Climate change]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic1_8000.png}}&
\subfloat[International research \& Education]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic2_8000.png}}\\
\subfloat[Chemistry]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic3_8000.png}}&
\subfloat[Economic \& Social science]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic4_8000.png}} &
\subfloat[Mathematics]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic5_8000.png}}\\
\subfloat[Molecular biology / Genetics]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic6_8000.png}} &
\subfloat[Materials]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic7_8000.png}}&
\subfloat[Cognitive neuroscience]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic8_8000.png}}\\
\subfloat[High energy physics]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic9_8000.png}}&
\end{tabular}
\caption{Wordclouds of topics of the USA (1994-1997)}
\end{figure}
\end{center}

\begin{center}
\begin{figure}
\begin{tabular}{rcl}
\subfloat[Applied Sciences]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic0_8000.png}} &
\subfloat[Environment \& Climate change]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic1_8000.png}}&
\subfloat[Materials \& Chemistry]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic2_8000.png}}\\
\subfloat[Biology]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic3_8000.png}}&
\subfloat[Information systems]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic4_8000.png}} &
\subfloat[STEM education]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic5_8000.png}}\\
\subfloat[Systems ?]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic6_8000.png}} &
\subfloat[Biology \& Evolution]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic7_8000.png}}&
\subfloat[Mathematics]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic8_8000.png}}\\
\subfloat[International conferences]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic9_8000.png}}&
\end{tabular}
\caption{Wordclouds of topics of the USA (1998-2001)}
\end{figure}
\end{center}

\begin{center}
\begin{figure}
\begin{tabular}{rcl}
\subfloat[Information systems]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic0_8000.png}} &
\subfloat[Education (in engineering)]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic1_8000.png}}&
\subfloat[Materials \& Chemistry]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic2_8000.png}}\\
\subfloat[International conferences]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic3_8000.png}}&
\subfloat[Biology \& Evolution]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic4_8000.png}} &
\subfloat[Green transportation]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic5_8000.png}}\\
\subfloat[Economic \& Social policy]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic6_8000.png}} &
\subfloat[Climate change]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic7_8000.png}}&
\subfloat[Materials]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic8_8000.png}}\\
\subfloat[Physics]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic9_8000.png}}&
\end{tabular}
\caption{Wordclouds of topics of the USA (2002-2006)}
\end{figure}
\end{center}

\begin{center}
\begin{figure}
\begin{tabular}{rcl}
\subfloat[STEM education]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic0_9000.png}} &
\subfloat[Computer \& Networking systems]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic1_9000.png}}&
\subfloat[Chemistry \& Materials science]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic2_9000.png}}\\
\subfloat[Climate change \ Environmental science]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic3_9000.png}}&
\subfloat[High energy physics]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic4_9000.png}} &
\subfloat[Atmospheric \& Ocean sciences]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic5_9000.png}}\\
\subfloat[Information systems]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic6_9000.png}} &
\subfloat[Mathematics]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic7_9000.png}}&
\subfloat[(Molecular) biology]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic8_9000.png}}\\
\subfloat[Economic \& Social policy]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic9_9000.png}}&
\end{tabular}
\caption{Wordclouds of topics of the USA (2007-2013)}
\end{figure}
\end{center}

\begin{center}
\begin{figure}
\begin{tabular}{rcl}
\subfloat[Biology]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic0_8000.png}} &
\subfloat[Climate Change / Geology]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic1_8000.png}}&
\subfloat[Sociology]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic2_8000.png}}\\
\subfloat[STEM education]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic3_8000.png}}&
\subfloat[Information systems]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic4_8000.png}} &
\subfloat[Chemical \& transport systems]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic5_8000.png}}\\
\subfloat[Materials \& Chemistry]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic6_8000.png}} &
\subfloat[Materials \& Mechanical engineering]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic7_8000.png}}&
\subfloat[Mathematics]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic8_8000.png}}\\
\subfloat[International research]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic9_8000.png}}&
\end{tabular}
\caption{Wordclouds of topics of the USA (2014-2017)}
\end{figure}
\end{center}
